---
title: "Recipe Preparation and Cook Time Calculator"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(gtsummary,ggplotly,tidyverse,tidytext)
```

## Primary Aim

The aim of this project is  to create a function that calculates the time of preparation and cooking based on the ingredients that the user will enter. The interface will be an `RShiny` app that
prompts the use for the ingredients.  The app will then estimate preparation and cooking time.

I will use the data set below to find the relationship between ingredients and
preparation time an cooking time.  Once this relationship has been modeled, 
the app will be able to calculate the prep and cook time for the ingredients the user
enters.

I will use tidytext to analyze the recipe data.  Then I will use tidymodels to get a mathematical 
model of the relationships between the ingredients listed and the outcome times.

The user interface will be written using `RShiny`.


I will use the data described below to fit a model predicting preparation and cooking time.
The package tidytext will be used to create the features.  The package tidymodels will 
be used to create the model and fit the model on the ingredients the user enters.

### The Data

The data is consisting of 255 recipes from India which each recipes contains some variables which are (name of the Recipes,Ingredients,Diet,Preparation time, cooking time,Flavor, Course,State(the origin of the food),region(location)).

## Proof of Concept

The steps to complete this analysis require:

* Find a training data set (`indian_food.csv`)
* Explore the training data set to find good features and descriptions (given below)
* Use `tidytext` to create features from the ingredients listed in the training data set.
* Use the features created and tidymodels to fit a model.
* test the model
* write an `RShiny` interface that askes the user for a list of ingredient
* Take the ingredients given and then use the fitted model to calculate the prep and cooking time for that recepe.

### Data Exploration


This is the training data set.

```{r}
d <- read.csv(here::here("data-raw","indian_food.csv"))
d %>% head
```

Summary of the data.  what's in the data set. 

```{r}
d %>% 
  select(-name, -ingredients) %>% 
  tbl_summary()
```

count the NO. of recopies per state 

```{r}
d %>% 
  count(state) %>% 
  arrange(desc(n))
```
plot the relationship btw perp time and cook time by course 

```{r}
d %>% 
  ggplot(aes(x=prep_time, y = cook_time))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~course)
```
the average of prep time by state 

```{r}
d %>% 
  
  ggplot(aes(x = prep_time, y = state))+
  geom_bar(stat = 'summary', fun = mean)
```
average prep time by diet 
```{r}
d %>% 
  ggplot(aes(x = prep_time, y = diet))+
  geom_bar(stat = "summary", fun = mean)
```


```{r}
d %>% 
  ggplot(aes(x = prep_time, y = course))+
  geom_bar(stat = "summary", fun.y = "mean")
```

### Feature Extraction

Start of feature extraction froom the ingredients list.
This shows how individual ingredients can be extracted to features.

```{r}
d %>% 
  select(name,prep_time, cook_time, ingredients) %>% 
  mutate(ind = 1) %>% 
  separate_rows(ingredients, sep = ',') %>% 
  pivot_wider(names_from = 'ingredients', values_from = "ind") %>% 
  mutate(across(is_double, ~if_else(is.na(.x),0,1)))
```



## Challenges and To-Do:
* in some point I will have to create  more data sets of recipes to make the modal better 
* what I will do if the user enters ingredient that are not in the data set.
* what other info besides ingredient should the user require to enter
* To fix the error that I will encounter in my code.
* Finding online cook book with more recipes to add them in my training data.

## To Do

* add data set (10\14)
*extract features using tidytext (10\21)
*Fit the models using tidymodals(10\28)
*create Rshiny interface(11\5)
*users testing the package (11\10)
* publish the package in the internet (11\13)

